Project-II by Group MexicoCity

### 2014-12-14 Project 2/report/paper.tex
report final update 2

\begin{abstract}
In this project we are given two problems: that of predicting the music listening counts for a given set of users based on their previous listening behaviour and friendship relations; and that of recognizing the presence of people no images. This report discusses preliminary observations on the given training data, and then results of testing various ML methods for prediction / classification.
\end{abstract}

@@

\subsection{Penalize Logistic regression (cross-validation for $\lambda$}
Penalized logistic regression was cross-validated (for the lambda parameter) to see which setting gives the best estimated TPR. The error metric taken was 1-TPR, which made simple sense. $\lambda$ values between $10^{-3}$ and $10^2$ were tested, 15 of them, and using 15 different seeds. So a total of $15 \cdot 15=225$ gradient descent runs for PLR were tried, giving the following plot (Figure \ref{fig:TEPLR})
It seems that, roughly, the more we increase lambda, the better our test error equivalent (1-TPR, which is actually the False Negative Rate) is.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.6]{images/PLRKCVplot.png}
\caption{Test error PLR with various $\lambda$}
\label{fig:TEPLR}
\end{figure} For $\lambda$ = 44, we deem it the test error no longer decreases significantly and it’s sufficiently good at 0.1849 (this corresponds to a TPR of 0.8151). This would be the best possible variant in the Logistic regression family to use. It remains to be seen at this point, however, if other ML methods can do better, especially after all their variants have been cross-validated (NN with various dropouts and $L_2$ weight penalties for instance). (red curves show the 1-TPR for test set, using model trained on a different training set, for each lambda, each curve being the result of a different seed, the bold curve being the average).

>>>>

\begin{abstract}
In this project we are given two problems: that of predicting the music listening counts for a given set of users based on their previous listening behaviour and friendship relations; and that of recognizing the presence of people in images. This report discusses preliminary observations on the given training data, and then results of testing various ML methods for prediction / classification.
\end{abstract}

@@

\subsection{Penalize Logistic regression (cross-validation for $\lambda$)}
Penalized logistic regression was cross-validated (for the lambda parameter) to see which setting gives the best estimated TPR. The error metric taken was 1-TPR, which made simple sense. $\lambda$ values between $10^{-3}$ and $10^2$ were tested, 15 of them, and using 15 different seeds. So a total of $15 \cdot 15=225$ gradient descent runs for PLR were tried, giving the following plot (Figure \ref{fig:TEPLR})
It seems that, roughly, the more we increase lambda, the better our test error equivalent (1-TPR, which is actually the False Negative Rate) is.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.6]{images/PLRKCVplot.png}
\caption{Test error PLR with various $\lambda$}
\label{fig:TEPLR}
\end{figure} For $\lambda$ = 44, we deem it the test error no longer decreases significantly and it’s sufficiently good at 0.1849 (this corresponds to a TPR of 0.8151). This would be the best possible variant in the Logistic regression family to use. It remains to be seen at this point, however, if other ML methods can do better, especially after all their variants have been cross-validated (NN with various dropouts and $L_2$ weight penalties for instance). (red curves show the 1-TPR for test set, using model trained on a different training set, for each lambda, each curve being the result of a different seed, the bold curve being the average).
